Plant-pollintor networks worldwide are composed by the same specific building blocks

### 2021-05-19 Draft/Draft.Rmd
Update Draft.Rmd

# Mean percentile and SE taking into account the study system
plant_codes <- plant_position_percentiles_filtered$position %>% unique()
plant_means <- tibble(position = plant_codes)
plant_means$mean <- NA
plant_means$SE <- NA

@@

  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
            data = subset(plant_position_percentiles_filtered,
                          position == plant_codes[i.pos]))

  plant_means$mean[i.pos] <- fixed.effects(m) %>% unname()
  plant_means$SE[i.pos] <- sqrt(diag(vcov(m)))

@@

GF_plant_pos <- ggplot(NULL) + 
  geom_point(data = plant_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG,ncol = 5)+
  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile",title = "Plants")+
  theme_bw()+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

@@

# Mean percentile and SE taking into account the study system
pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
pollinator_means <- tibble(position = pollinator_codes)
pollinator_means$mean <- NA
pollinator_means$SE <- NA

for(i.pos in 1:length(pollinator_codes)){

  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
            data = subset(pollinator_position_percentiles_filtered,
                          position == pollinator_codes[i.pos]))

  pollinator_means$mean[i.pos] <- fixed.effects(m) %>% unname()
  pollinator_means$SE[i.pos] <- sqrt(diag(vcov(m)))

@@

GF_poll_pos <- ggplot(NULL) + 
  geom_point(data = pollinator_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG,ncol = 5)+
  geom_errorbar(data = pollinator_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = pollinator_means,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile", title = "Pollinators")+
  theme_bw()+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

@@

ggarrange(GF_plant_pos,GF_poll_pos,
          ncol = 1, nrow = 2,heights = c(.9, 1.4))

>>>>

# Mean percentile and SE taking into account the study system
plant_codes <- plant_position_percentiles_filtered$position %>% unique()
plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
plant_means$mean <- NA
plant_means$SE <- NA

@@

  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
            data = plant_position_percentiles_filtered %>%
                          filter(position == plant_codes[i.pos]))

  temp <- fixed.effects(m) %>% unname()
  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
                                                                     temp[1]+temp[2],
                                                                     temp[1]+temp[3],
                                                                     temp[1]+temp[4],
                                                                     temp[1]+temp[5]) ## to get real means per FG
  temp <- sqrt(diag(vcov(m)))
  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
                                                                  temp[1]+temp[2],
                                                                  temp[1]+temp[3],
                                                                  temp[1]+temp[4],
                                                                  temp[1]+temp[5])

@@

GF_plant_pos <- ggplot(NULL) + 
  geom_point(data = plant_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  facet_wrap(~Node_FG,ncol = 5)+
  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile",title = "Plants")+
  theme_bw()+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

@@

# Mean percentile and SE taking into account the study system
pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
pollinator_means$mean <- NA
pollinator_means$SE <- NA
pollinator_means_reordered <- NULL
for(i.pos in 1:length(pollinator_codes)){
  print(i.pos)
  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
            data = pollinator_position_percentiles_filtered %>%
                          filter(position == pollinator_codes[i.pos]))

  temp <- fixed.effects(m) %>% unname()
  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)

  pollinator_means_aux$mean <- c(temp[1],
                                 temp[1]+temp[2],
                                 temp[1]+temp[3],
                                 temp[1]+temp[4],
                                 temp[1]+temp[5],
                                 temp[1]+temp[6],
                                 temp[1]+temp[7],
                                 temp[1]+temp[8],
                                 temp[1]+temp[9]) ## to get real means per FG

  temp <- sqrt(diag(vcov(m)))
  pollinator_means_aux$SE <- c(temp[1],
                               temp[1]+temp[2],
                               temp[1]+temp[3],
                               temp[1]+temp[4],
                               temp[1]+temp[5],
                               temp[1]+temp[6],
                               temp[1]+temp[7],
                               temp[1]+temp[8],
                               temp[1]+temp[9])

  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)

@@

# There are lower limits (mean - SE) smaller than 0 (see Other insects)
# We set the lower limit of those error bars to zero

pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0

GF_poll_pos <- ggplot(NULL) + 
  geom_point(data = pollinator_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = pollinator_means_reordered, aes(x = as.factor(position), ymin=lower,
                                                       ymax=mean+SE), 
                width=1.0,size=1)+
  facet_wrap(~Node_FG,ncol = 5)+
  geom_point(data = pollinator_means_reordered,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile", title = "Pollinators")+
  theme_bw()+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

@@

ggarrange(GF_plant_pos,GF_poll_pos,
          ncol = 1, nrow = 2,heights = c(.90, 1.4))
